### 2016-07-03 lineups.Rnw
convergence description in write up

4. What parameters are in the output?
% ST: add how convergence is calculated. from RSiena manual. 
5. What are the results?
}
\begin{figure}
<<results1, fig.width=8, fig.height=6, out.width='\\linewidth', echo = FALSE, warning = FALSE>>=
l1 <- levels(lus_ests_truth$param_name)
l1 <- stringr::str_trim(gsub("2","", l1))
l1[5] <- "#pairs at doubly achieved distance"

>>>>

4. What parameters are in the output?
\st{In RSiena, the convergence of a non-rate parameter is determined through the simulated values from Phase 3 of the SienaFit algorithm. XXX more detail will be above later XXX  The simulations are compared to the observed values of the statistics observed in the data. The values from the simulations should be fairly close to the observed values, but because the fitting is done stochastically, deviations from statistics will not be exactly zero. Checking for convergence is based on a t-ratio of the average of these deviations to the standard deviation of these deviations. RSiena also performs an overall maximum convergence check by finding the maximum t-ratio value for any linear combination of the observed statistics.  According to the RSiena Manual, ``convergence is excellent when the overall maximum convergence ratio is less than 0.2", and for the non-rate parameters, the threshold for ``reasonable" convergence is set at 0.3 with excellent convergence when the t-ratio is less than or equal to 0.1 in absolute value. (\cite{RSiena}).
}

% ST: add how convergence is calculated. from RSiena manual. 
5. What are the results?
}
\begin{figure}
<<results1, fig.width=8, fig.height=6, out.width='\\linewidth', echo = FALSE, warning = FALSE>>=
l1 <- levels(lus_ests_truth$param_name)
l1 <- stringr::str_trim(gsub("2","", l1))
l1[5] <- "#pairs at doubly achieved distance"
